---
title: "getting individual's estimate of affect/valence/arousal"
format: html
editor: visual
---

#loading the packeges

```{r}
#| label: load-packages
#| include: false

library (ggplot2)
library(RColorBrewer)
library(reshape2)
library(tidyverse)
library(dplyr)
library(circlize)
library(leaps)
library(ggpubr)
library(ggstatsplot) # for box-plots with statistics
library(knitr)       # beautifying tables
library(ggsci) #colors
library(gridExtra)
library(NatParksPalettes)    # beautifying tables
```

#pe_abs_cue_affect_grid

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("new_cue_37.csv")%>%
  select(-pe, cue)
#colnames(a) <- c('Arousal', 'Valence', 'Expectation', 'Cue', 'sub')

```

```{r}
#smooth
pic <- ggplot(a, aes(x=pe_abs, y=value))+ 
  facet_grid(Affect~Cue)+
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  scale_colour_manual(values = c("#CB171D", "#2D74AC"))+
  geom_point(aes(fill = Cue), size = 2.5, alpha =0.7, shape = 21, color = 1)+ 
  geom_smooth(aes(fill = Cue, colour = Cue), method = 'lm', se = F, size= 1,
              fullrange = F, alpha = 0.3, show.legend = FALSE)+
  theme_bw()+
  #stat_cor(data=a, method = "spearman", show.legend=FALSE)+
  theme(panel.grid.major.y = element_blank(),
        legend.position = 'none',
        legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="Cue",y="Affect")
pic
#ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/pe_abs_cue_affect_grid.png", width = 8, height = 8)

```

#new sociability & ECG ISRSA with the behavirl model estimates

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
data <- read.csv('new_high_low_rsa.csv',header = T)%>%
  select(-aff_pe_low, -aff_pe_high,-aff_cue_low, -aff_cue_high, -hrvsd)
#colnames(data) <- c('ar_pe_low', 'ar_pe_high', "ar_cue_low", 'ar_cue_high', 'va_pe_low', 'va_pe_high', 'va_cue_low', 'va_cue_high','aff_pe_low', 'aff_pe_high', 'aff_cue_low', 'aff_cue_high',"EC", "PD", "SO", "SS", "hrvm", "hrvsd")
#write.csv(data,file = "~/Desktop/Emotional_Volatility/for_isrsa/new_high_low_rsa.csv",row.names = F)

#data <- read.csv('est_isc_33.csv',header = T)
library(GGally)
a <- ggcorr(data,label = TRUE, label_size = 3, label_round = 2, label_alpha = FALSE,
            nbreaks =11,
            method = c("all.obs", "spearman"))
a
ggsave(a, filename = "~/Desktop/Emotional_Volatility/fig3/corr_rdm_4.21.png", width = 10, height = 10)

```

#pop out the signifcant ones

```{r}
pic <- ggplot(data, aes(x=PD, y = va_cue_high))+ 
  #scale_colour_manual(values=natparks.pals("BryceCanyon", 4))+
  geom_point(size = 1.5, alpha = 0.6, color = '#E09891')+ 
  geom_smooth(method = 'lm', se = F, color = '#C1726B')+
  stat_cor(data = data, method = "pearson", 
           show.legend = FALSE)+ #remove the a
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
        legend.position = 'none',
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    legend.title = element_text(size=12), #change legend title font size
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="SO",y="Valence on Cue(low volatility)")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/so_va_cue_high.png", 
       width = 4, height = 4)
```

#beta estimates, 3-way ANOVA #estimates of cue

```{r}
#a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/high_low_est.csv")
a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/new_estimate_1.csv")%>%
  filter(Predictors == "Cue")%>%
  filter(Affect != "Affect")
a$est_z <- a$est%>%scale()
  
pic <- ggplot(data = a, 
              aes(x = Volatility, y = est, fill = Affect)) +
  geom_point(aes(x = Volatility, y = est, color = Affect), 
             position=position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7), size = 1, alpha = 0.6) +
  geom_boxplot(width = 0.7, outlier.shape = NA, alpha = 0.8, size = 0.8)+
  geom_hline(yintercept = 0, linetype="dashed",  size=0.4)+
  scale_fill_manual(values = c("#82709A", "#87A96D"))+
  scale_colour_manual(values = c("#82709A", "#87A96D"))+
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = "none",
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=10, color = "black"),
    axis.title.x=element_text(size=10),
    axis.title.y=element_text(size=10), 
    strip.text.x = element_text(size = 10),
    legend.box.background = element_rect(color = NA))+
  guides(color=guide_legend(title = "Volatility"))+
  #scale_y_continuous(limits = c(-0.5,1.5) )+ #坐标轴刻度标签和范围
  labs(title ="", x="Volatility",y="Model estimates of cue")+
  theme(text = element_text(family = "Helvetica"))
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/est_cue.png", 
       width = 4, height = 4)

```

#estimates of PE

```{r}
a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/new_estimate_1.csv")%>%
  filter(Predictors == "PE")%>%
  filter(Affect != "Affect")
a$est_z <- a$est%>%scale()
  
pic <- ggplot(data = a, 
              aes(x = Volatility, y = est, fill = Affect)) +
  geom_point(aes(x = Volatility, y = est, color = Affect), 
             position=position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7), size = 1, alpha = 0.6) +
  geom_boxplot(width = 0.7, outlier.shape = NA, alpha = 0.8, size = 0.8)+
  geom_hline(yintercept = 0, linetype="dashed",  size=0.4)+
  scale_fill_manual(values = c("#82709A", "#87A96D"))+
  scale_colour_manual(values = c("#82709A", "#87A96D"))+
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = "none",
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=10, color = "black"),
    axis.title.x=element_text(size=10),
    axis.title.y=element_text(size=10), 
    strip.text.x = element_text(size = 10),
    legend.box.background = element_rect(color = NA))+
  guides(color=guide_legend(title = "Volatility"))+
  #scale_y_continuous(limits = c(-0.5,1.5) )+ #坐标轴刻度标签和范围
  labs(title ="", x="Volatility",y="Model estimates of PE")+
  theme(text = element_text(family = "Helvetica"))
pic

ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/est_pe.png", width = 4, height = 4)

```

##valence&arousal bar graph by volatility

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/") 
a <- read.csv('4.24_interaction.csv')%>%
  select(arousal, valence, Volatility)

colnames(a) <- c('Arousal', 'Valence', 'Volatility')

b <- melt(data = a,id.vars=c("Volatility"),variable.name="Affect",
          value.name="values")

dodge <- position_dodge(width=.8)
pbar <- ggplot(b, aes(x = Affect, y = values, 
                      fill = factor(Volatility, level = c('low', 'medium', 'high'))))+
  #adding bars
  stat_summary(fun=mean, geom = "bar",
               fun.args = list(mult = 1), width = 0.8, position = dodge, alpha = 0.75, colour = 1, size = 0)+
  stat_summary(fun.data = 'mean_se', geom = "errorbar",
               width = 0.15, position = position_dodge( .8), size = 0.4)+
  scale_fill_manual(values = c("#D3D0CB", "#72A2BF", "#33658A"))+
  scale_colour_manual(values = c("#D3D0CB", "#72A2BF", "#33658A"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.background=element_blank(), axis.line=element_line(color="black"),)+
  theme(legend.position='none')+
  coord_cartesian(ylim = c(30, 75)) +# scales of y
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    legend.title = element_text(size=12), #change legend title font size
    legend.text = element_text(size=12),
    legend.direction = 'vertical', #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="Affect",y="Score")+
  guides(color=guide_legend(title = "Volatility"))
ggsave(pbar, filename = "~/Desktop/Emotional_Volatility/fig3/4.24volatility_bar.png", 
       width = 4, height = 4)
pbar


```

```{r}
####
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("forfig.csv")%>%
  select(-pe)
colnames(a) <- c('Arousal', 'Valence', 'Expectation', 'Cue', 'sub')
a <- melt(data = a,id.vars=c("sub", "Cue"),variable.name="ratings",value.name="values")

dodge <- position_dodge(width=.8)
pbar <- ggplot(a, aes(x = ratings, y = values, 
                      fill = Cue))+
  #adding bars
  stat_summary(fun=mean, geom = "bar",
               fun.args = list(mult = 1), width = 0.8, position = dodge, alpha = 0.65, colour = 1, size = 0)+
  stat_summary(fun.data = 'mean_se', geom = "errorbar",
               width = 0.15, position = position_dodge( .8), size = 0.4)+
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  #scale_fill_brewer(palette = "Paired") +
  # scale_colour_brewer(palette = "Paired") +
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.background=element_blank(), axis.line=element_line(color="black"),)+
  theme(legend.position=c(0.75,0.9))+
  coord_cartesian(ylim = c(20, 75)) +# scales of y
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    legend.title = element_text(size=12), #change legend title font size
    legend.text = element_text(size=12),
    legend.direction = 'vertical', #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="Rating items",y="Score")+
  guides(color=guide_legend(title = "Cue"))
ggsave(pbar, filename = "~/Desktop/Emotional_Volatility/fig3/value_cue_box_4.24.png", 
       width = 4, height = 4)
pbar

```

#behaviral measures ISC and the trait ISC

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
data <- read.csv('behav_isc_37.csv',header = T)
#colnames(data) <- c('ar_pe_low', 'ar_pe_high', "ar_cue_low", 'ar_cue_high', 'va_pe_low', 'va_pe_high', 'va_cue_low', 'va_cue_high','aff_pe_low', 'aff_pe_high', 'aff_cue_low', 'aff_cue_high',"EC", "PD", "SO", "SS", "hrvm", "hrvsd")
#write.csv(data,file = "~/Desktop/Emotional_Volatility/for_isrsa/new_high_low_rsa.csv",row.names = F)

#data <- read.csv('est_isc_33.csv',header = T)
library(GGally)
a <- ggcorr(data,label = FALSE, label_size = 3, label_round = 2, label_alpha = TRUE,
            nbreaks =11,
            method = c("all.obs", "spearman"))
a
ggsave(a, filename = "~/Desktop/Emotional_Volatility/fig3/corr_rsm_4.21.png", width = 6, height = 6)

```

#pop out the signifcant ones

```{r}
pic <- ggplot(data, aes(x=SO, y = Arousal))+ 
  #scale_colour_manual(values=natparks.pals("BryceCanyon", 4))+
  geom_point(size = 1.5, alpha = 0.6, color = '#E09891')+ 
  geom_smooth(method = 'lm', se = F, color = '#C1726B')+
  stat_cor(data = data, method = "spearman", 
           show.legend = FALSE)+ #remove the a
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
        legend.position = 'none',
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    legend.title = element_text(size=12), #change legend title font size
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="SO similarity",y="Arousal similarity")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/so_ar_isrsa.png", 
       width = 4, height = 4)
```

#interaction analysis for the behaviral models

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("4.24_interaction.csv")
pic <- ggplot(a, aes(x=pe, y=resi_ar),
              color = Cue, fill = Cue)+ 
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  scale_colour_manual(values = c("#CB171D", "#2D74AC"))+
  geom_point(aes(fill = Cue, colour = Cue), size = 1, alpha =0.5)+ 
  geom_smooth(aes(fill = Cue, colour = Cue), method = 'lm', se = T, linewidth= 1,
              fullrange = F, alpha = 0.3, show.legend = FALSE)+
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
       legend.position = 'none',
        legend.direction = 'vertical', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="PE",y="Arousal")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/4.24_ar_interaction.png", width = 4, height = 4)



```

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("4.24_interaction.csv")
pic <- ggplot(a, aes(x = pe, y = resi_va),
               color = factor(Volatility, level = c('low', 'medium', 'high')),  fill = factor(Volatility, level = c('low', 'medium', 'high')))+ 
  scale_fill_manual(values = c("#D3D0CB", "#33658A", "#2F4858"))+
  scale_colour_manual(values = c("#D3D0CB","#33658A", "#2F4858"))+
  geom_point(aes(color = factor(Volatility, level = c('low', 'medium', 'high')),  fill = factor(Volatility, level = c('low', 'medium', 'high'))), size = 1, alpha =0.5)+ 
  geom_smooth(aes(color = factor(Volatility, level = c('low', 'medium', 'high')),  fill = factor(Volatility, level = c('low', 'medium', 'high'))), method = 'lm', se = T, linewidth= 1,
              fullrange = F, alpha = 0.3, show.legend = FALSE)+
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
        legend.position = 'none',
        legend.direction = 'vertical', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  labs(title ="", x="PE",y="Valence")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/4.24_va_interaction_6.png", width = 4, height = 4)



```

#5.10: interaction of volatility & cue on arousal, line graph

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/") 
#reg <- read.csv('new_cue_vola_37_melt.csv')%>% select(arousal, valence, Volatility)
#a <- melt(reg, na.rm = FALSE, value.name = 'affect', id = 'Volatility')
#write.csv(a,file = "~/Desktop/Emotional_Volatility/for_isrsa/melted_affect.csv",row.names = F)
a <- read.csv('melted_affect_5.10.csv')
pic <- ggplot(data = a, 
              aes(x = factor(Volatility, level = c('low', 'medium', 'high')),
                  y = value, color = Cue,group = Cue )) +
  geom_line(size = 1) +
  geom_point(aes(y = value, color = Cue),size = 3)+
  geom_errorbar(aes(ymin=value - se, ymax=value + se, width=.2),size = 1)+
  #introdataviz::geom_flat_violin(position = position_nudge(x = 0.2, y = 0), alpha = 0.5) +
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  scale_colour_manual(values = c("#CB171D", "#2D74AC"))+
  # custom colours and theme
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = 'none',
        legend.direction = 'vertical', 
        legend.background = element_rect(fill = "white", color = "white"))+
theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    legend.title = element_text(size=12), #change legend title font size
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  #coord_cartesian(ylim = c(-65, 100)) +# scales of y
  labs(title ="", x="Volatility",y="Arousal")+
  theme(text = element_text(family = "Helvetica"))
#ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/5.10_interaction_arousal.png",width = 4, height = 4)
pic
```

#5.10: interaction of PE&Cue&Reward on valence

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("cue_vola_reward_37.csv")%>%filter(reward == 1)
pic <- ggplot(a, aes(x=pe, y=valence),
              color = Cue, fill = Cue)+ 
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  scale_colour_manual(values = c("#CB171D", "#2D74AC"))+
  stat_cor(data = a%>%filter(Cue == "happy"), method = "pearson", label.y = 100)+
  stat_cor(data = a%>%filter(Cue == "sad"), method = "pearson", label.y = 0.8)+
  geom_point(aes(fill = Cue, colour = Cue), size = 1, alpha =0.5)+ 
  geom_smooth(aes(fill = Cue, colour = Cue), method = 'lm', se = T, linewidth= 1,
              fullrange = F, alpha = 0.3, show.legend = FALSE)+
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
       legend.position = 'none',
        legend.direction = 'vertical', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
    #coord_cartesian(xlim = c(-65, 80)) +# scales of y
  labs(title ="", x="PE",y="Valence")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/6.20_interaction_va_1.png", width = 4, height = 4)



```

#5.10: interaction of PE&Cue&Reward on arousal

```{r}
setwd("~/Desktop/Emotional_Volatility/for_isrsa/")
a <- read.csv("cue_vola_reward_37.csv")%>%filter(reward == 0)
pic <- ggplot(a, aes(x=pe, y=arousal),
              color = Cue, fill = Cue)+ 
  scale_fill_manual(values = c("#CB171D", "#2D74AC"))+
  scale_colour_manual(values = c("#CB171D", "#2D74AC"))+
 geom_point(aes(fill = Cue, colour = Cue), size = 1, alpha =0.5)+ 
  geom_smooth(aes(fill = Cue, colour = Cue), method = 'lm', se = T, linewidth= 1,
              fullrange = F, alpha = 0.3, show.legend = FALSE)+
    stat_cor(data = a%>%filter(Cue == "happy"), method = "pearson",label.y = 100)+
  stat_cor(data = a%>%filter(Cue == "sad"), method = "pearson", label.y = 0.8)+
  theme_classic()+
  theme(panel.grid.major.y = element_blank(),
       legend.position = 'none',
        legend.direction = 'vertical', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
    #coord_cartesian(xlim = c(-65, 80)) +# scales of y
  labs(title ="", x="PE",y="Arousal")
pic
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/6.20_interaction_ar_0.png", width = 4, height = 4)



```

#5.12 estimates plots #beta estimates, 3-way ANOVA #estimates of cue

```{r}
#a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/high_low_est.csv")
a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/5.10_estimates.csv")%>%
  filter(Predictors == "Cue")
a$est_z <- a$est%>%scale()
  
pic <- ggplot(data = a, 
              aes(x = Volatility, y = est, fill = Affect)) +
  geom_point(aes(x = Volatility, y = est, color = Affect), 
             position=position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7), size = 1, alpha = 0.6) +
  geom_boxplot(width = 0.7, outlier.shape = NA, alpha = 0.8, size = 0.8)+
  geom_hline(yintercept = 0, linetype="dashed",  size=0.4)+
  scale_fill_manual(values = c("#82709A", "#87A96D"))+
  scale_colour_manual(values = c("#82709A", "#87A96D"))+
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = "none",
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  guides(color=guide_legend(title = "Volatility"))+
  scale_y_continuous(limits = c(-10,100) )+ #坐标轴刻度标签和范围
  labs(title ="", x="Volatility",y="Model estimates of cue")+
  theme(text = element_text(family = "Helvetica"))
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/5.10_est_cue.png", 
       width = 4, height = 4)

pic
```

#estimates of reward

```{r}
#a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/high_low_est.csv")
a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/5.10_estimates.csv")%>%
  filter(Predictors == "Reward")
a$est_z <- a$est%>%scale()
  
pic <- ggplot(data = a, 
              aes(x = Volatility, y = est, fill = Affect)) +
  geom_point(aes(x = Volatility, y = est, color = Affect), 
             position=position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7), size = 1, alpha = 0.6) +
  geom_boxplot(width = 0.7, outlier.shape = NA, alpha = 0.8, size = 0.8)+
  geom_hline(yintercept = 0, linetype="dashed",  size=0.4)+
  scale_fill_manual(values = c("#82709A", "#87A96D"))+
  scale_colour_manual(values = c("#82709A", "#87A96D"))+
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = "none",
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  guides(color=guide_legend(title = "Volatility"))+
  scale_y_continuous(limits = c(-10,100) )+ #坐标轴刻度标签和范围
  labs(title ="", x="Volatility",y="Model estimates of reward")+
  theme(text = element_text(family = "Helvetica"))
ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/5.10_est_re.png", 
       width = 4, height = 4)

pic
```

#estimates of PE

```{r}
a <- read.csv("~/Desktop/Emotional_Volatility/for_isrsa/5.10_estimates.csv")%>%
  filter(Predictors == "PE")
a$est_z <- a$est%>%scale()
  
pic <- ggplot(data = a, 
              aes(x = Volatility, y = est, fill = Affect)) +
  geom_point(aes(x = Volatility, y = est, color = Affect), 
             position=position_jitterdodge(jitter.width = 0.08, dodge.width = 0.7), size = 1, alpha = 0.6) +
  geom_boxplot(width = 0.7, outlier.shape = NA, alpha = 0.8, size = 0.8)+
  geom_hline(yintercept = 0, linetype="dashed",  size=0.4)+
  scale_fill_manual(values = c("#82709A", "#87A96D"))+
  scale_colour_manual(values = c("#82709A", "#87A96D"))+
  theme_classic() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = "none",
        #legend.direction = 'horizontal', 
        legend.background = element_rect(fill = "white", color = "white"))+
  theme(#plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
    axis.text=element_text(size=14, color = "black"),
    axis.title.x=element_text(size=18),
    axis.title.y=element_text(size=18), 
    strip.text.x = element_text(size = 18),
    strip.text.y = element_text(size = 18),#change grid font
    legend.text = element_text(size=12), #change legend text font size
    legend.box.background = element_rect(color = NA))+
  guides(color=guide_legend(title = "Volatility"))+
  scale_y_continuous(limits = c(-0.4,0.5) )+ #坐标轴刻度标签和范围
  labs(title ="", x="Volatility",y="Model estimates of PE")+
  theme(text = element_text(family = "Helvetica"))

ggsave(pic, filename = "~/Desktop/Emotional_Volatility/fig3/5.10_est_pe.png", width = 4, height = 4)

pic

```
